### 2020-05-30 README.Rmd
tidy readme

---
output: github_document
---

@@

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

The goal of neonstore is to provide access and persistent storage of NEON data tables

@@

```{r output="hide"}
meta <- neon_index("brd_countdata") 
meta
```

```{r echo=FALSE}
# pretty-print
tibble::as_tibble(meta)
```

@@

```{r}
brd_countdata <- neon_read(meta)
```

>>>>

---
output: 
  github_document:
    df_print: tibble
---

@@

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(neonstore)

@@

The goal of neonstore is to provide access and persistent storage of NEON data tables.

@@

```{r}
meta <- neon_index("brd_countdata") 
meta
```

@@

```{r message = FALSE}
brd_countdata <- neon_read(meta)
brd_countdata
```
